Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-08-25 manuscript.tex
Added figure to show when fails
Calculate the effect at a low height and show effect. The use higher
order.
Need better plot. Maybe use Cartopy.
Caption for glq fail example fig

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height and the Gauss-Legendre Quadrature order
        (number of nodes in each dimension).
        The $g_{xy}$ component caused by a
        $7^\circ \times 7^\circ \times 20\ km$ tesseroid
        with $2.67\ g.cm^{-3}$ density
        and top at $z=0$
        was calculated on a regular grid
        at different heights and using different orders.
        The GLQ order used was the same for all three dimensions.
        a) At $400\ km$ height and order 2, the effect is similar to that
        presented by \citet{Asgharzadeh2007}. b) At $150\ km$ height and order
        2, the effect resembles that of four point sources located at the GLQ
        nodes. c) At $150\ km$ but with a higher order of 30, the effect is
        again similar to the maps in \citet{Asgharzadeh2007}.
    }
    \label{fig:sample}
\end{figure}
